---
title: "Letters to Remove List"
output: html_notebook
---


```{r message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(tidygraph)
library(igraph)
library(DT)
library(ggraph)
library(snakecase)
library(kableExtra)
library(cowplot)

location <- read_csv("~/Downloads/EMLO/location.csv", col_types = cols(.default = "c"))
person <- read_csv("~/Downloads/EMLO/person.csv", col_types = cols(.default = "c"))
work <- read_csv("~/Downloads/EMLO/work.csv", col_types = cols(.default = "c"))

colnames(location) = to_snake_case(colnames(location))
colnames(person) = to_snake_case(colnames(person))
colnames(work) = to_snake_case(colnames(work))

```

## EMLO Recon Duplicates

This first list of duplicates is from a list produced by EMLO recon matching tool. I make a network, assign each component an ID, and keep only one from each component. The downside is there's no choice over which to keep. 

```{r message=FALSE, warning=FALSE, include=FALSE}

matches = readxl::read_xlsx('EMLO_Matched_Works_2020.6.4.xlsx')

emlo_dupes  = matches %>% select(2) %>% separate(1, into = c('X1','X2', 'X3','X4'))

edgelistdupes = emlo_dupes %>% pivot_longer(names_to = 'match', values_to = 'id', cols = 2:4) %>% select(-match) %>% filter(!is.na(id))

to_keep = edgelistdupes %>% graph_from_data_frame(directed = F) %>% as_tbl_graph() %>% mutate(comp= group_components(type = 'weak')) %>% activate(nodes) %>% as_tibble() %>% distinct(comp, .keep_all = T) %>% pull(name)

emlo_dupes_to_remove = c(emlo_dupes$X1, emlo_dupes$X2,emlo_dupes$X3, emlo_dupes$X4) %>% 
  as_tibble() %>% 
  mutate(value = trimws(value)) %>% 
  filter(!is.na(value)) %>% distinct(value) %>% filter(! value %in% to_keep) %>% pull(value)

emlo_dupes_to_check = c(emlo_dupes$X1, emlo_dupes$X2,emlo_dupes$X3, emlo_dupes$X4) %>% 
  as_tibble() %>% 
  mutate(value = trimws(value)) %>% 
  filter(!is.na(value)) %>% distinct(value) %>% pull(value)

```


This lists all letters sent on the same day with the same sender and recipient, which are also _not_ in the same catalogue. See checks below: nearly all seem to be genuine duplicates, though there are some which are different versions of the same letter. 

```{r message=FALSE, warning=FALSE, include=FALSE}


possible_dupes = work %>% 
  filter(standard_gregorian_date>'1590-01-01') %>% 
  filter(standard_gregorian_date<'1720-01-01') %>%
  group_by(standard_gregorian_date, author_emlo_id, recipient_emlo_id) %>% 
  add_tally() %>% 
  filter(n!=1) %>% 
  filter(n<4) %>% 
  group_by(standard_gregorian_date, author_emlo_id, recipient_emlo_id) %>% 
  summarise(all_cats = paste0(original_catalogue_name, collapse = ';'), emlo_letter_id_number) %>% 
  separate(all_cats, into = c('cat1', 'cat2', 'cat3', 'cat4'), sep = ';') %>% 
  filter(cat1 != cat2) %>%
  arrange(standard_gregorian_date) %>% 
  pull(emlo_letter_id_number)

possible_dupes_distinct_to_remove = work %>% 
  filter(standard_gregorian_date>'1590-01-01') %>% 
  filter(standard_gregorian_date<'1720-01-01') %>%
  filter(!emlo_letter_id_number %in% emlo_dupes_to_remove) %>% 
  filter(!emlo_letter_id_number %in% abstract_same_dupes)%>%
  group_by(standard_gregorian_date, author_emlo_id, recipient_emlo_id) %>% 
  add_tally() %>% 
  filter(n!=1) %>% 
  filter(n<4) %>% group_by(standard_gregorian_date, author_emlo_id, recipient_emlo_id) %>% 
  summarise(all_cats = paste0(original_catalogue_name, collapse = ';'), emlo_letter_id_number) %>% separate(all_cats, into = c('cat1', 'cat2', 'cat3', 'cat4'), sep = ';') %>% filter(cat1 != cat2) %>%
  arrange(standard_gregorian_date) %>% 
  distinct(author_emlo_id, recipient_emlo_id, standard_gregorian_date, .keep_all = T) %>% 
  pull(emlo_letter_id_number)

bcc_poss_dupes = work %>% 
  filter(emlo_letter_id_number %in% possible_dupes) %>% 
  filter(original_catalogue_name == 'Bodleian card catalogue') %>% pull(emlo_letter_id_number)
```

## Dummy catalogues

Several catalogues are 'tests' and include unfinished or duplicated records. For now, we remove letters from these catalogues.

```{r}

test_cats = c('Test_Pennant (test)', 'TESTS_Bayle', 'Test_Metadata test', 'TEST_Newton', 'Coornhert, Dirck Volckertszoon (test)')

test_cat_letter_ids = work %>% filter(original_catalogue_name %in% test_cats) %>% pull(emlo_letter_id_number)

```

## Optional step - Unknowns

There are lots of 'unknown' authors and recipients. We _could_ just remove these letters entirely because otherwise unknowns may be inaccurately collapsed into the same person, affecting metrics. We produce a second version of the 'to remove' list, with these unknowns added.

```{r message=FALSE, warning=FALSE, include=FALSE}
# First a list of IDs used for unknown senders or recipients to filter out:
unknowns = c('903934','23155', '6854', '853', '923980', '270', '300827', '901925', '906141')

# Next, a list of other IDs marked with either unknown or unidentified. Not necessarily to be taken out but could be split?

# unknown_list = person %>% 
#   filter(str_detect(person_primary_name_in_emlo,'(?i)unknown') |str_detect(person_primary_name_in_emlo,'(?i)unidentified') ) %>% pull(emlo_person_id)
# 
# unknowns = c(unknowns,unknown_list)

# Add letter IDs to a list where either sender or receiver are in these unknowns:

unknown_letters = work %>% filter(author_emlo_id %in% unknowns | recipient_emlo_id %in% unknowns) %>% pull(emlo_letter_id_number)


```

## Create full list to be removed

Create a text file with one record to be removed per line. This first includes all emlo recon duplicates, all posible duplicates based on identical date, sender and recipient, all with an unknown/unidentified sender or recipient, and all letters in test catalogues.


```{r}
c(emlo_dupes_to_remove, abstract_same_dupes, possible_dupes, test_cat_letter_ids,unknown_letters) %>% as_tibble() %>% distinct(value) %>% write_csv('to_remove_list_with_unknown.csv')
```

Without unknowns:

```{r}
c(emlo_dupes_to_remove, abstract_same_dupes, possible_dupes, test_cat_letter_ids) %>% as_tibble() %>% distinct(value) %>% write_csv('to_remove_list.csv')
```

Create a version of the work.csv with duplicates (only those I found, not including EMLO recon duplicates) for sorting and checking.

```{r}
work %>% 
  mutate(poss_dupe = ifelse(emlo_letter_id_number %in% emlo_dupes_to_check, 'no', ifelse(emlo_letter_id_number %in% possible_dupes, 'yes', 'no'))) %>% arrange(standard_gregorian_date, author, recipient) %>%  mutate(order = 1:nrow(.)) %>% select(order, everything()) %>%
  write_csv('work_with_poss_dupes.csv', na = '')
```

## Some checks:

http://emlo.bodleian.ox.ac.uk/profile/work/28b28649-cf73-4cd5-b6bd-3633e9507557
http://emlo.bodleian.ox.ac.uk/profile/work/b5b49138-233b-420c-8739-f9390a6f4e9c

Same content (used Google translate on the latin transcription and compared to the Bodleian abstract)
http://emlo.bodleian.ox.ac.uk/profile/work/b725d029-4968-4015-8b9c-152d5df77a18
http://emlo.bodleian.ox.ac.uk/profile/work/5925b225-601c-444e-89cf-f39278c951a2

Same shelfmark:
http://emlo.bodleian.ox.ac.uk/profile/work/3389edaf-8810-4b84-863f-1121c79aa5c6
http://emlo.bodleian.ox.ac.uk/profile/work/1f182425-aeba-4d53-9588-ef251bf4f5a8


Between Peiresc and Dupuy:
http://emlo.bodleian.ox.ac.uk/profile/work/479c6266-43cb-4ed3-af47-21e185b1401a
http://emlo.bodleian.ox.ac.uk/profile/work/a348c752-9ace-4e1c-b1d3-3f1d041fd993

This may not be a duplicate? 
Vossius, Gerardus Joannes
Pontanus, Johannes Isacius
http://emlo.bodleian.ox.ac.uk/profile/work/df297979-1ba0-4d4d-9135-2126d3fe78c3
http://emlo.bodleian.ox.ac.uk/profile/work/7294fe80-69aa-4b0c-97c3-aef5db70d3ec

Rubens, Peter Paul
Peiresc, Nicolas-Claude Fabri de
http://emlo.bodleian.ox.ac.uk/profile/work/82ac3d43-45e6-45ab-8fea-52cca2d5f34d
http://emlo.bodleian.ox.ac.uk/profile/work/3aa2b609-cfc2-4cdf-b54d-2e3e3a7a736f

Sometimes they are similar but different transcriptions/letters:
http://ckcc.huygens.knaw.nl/epistolarium/letter.html?id=huyg001/0263
http://ckcc.huygens.knaw.nl/epistolarium/letter.html?id=barl001/0019

Ussher letters - matches one of the manuscript copies
http://emlo.bodleian.ox.ac.uk/profile/work/eb3df7ee-6f5f-4681-9127-d7e1147a16df
http://emlo.bodleian.ox.ac.uk/profile/work/ee479540-da0c-4f12-840a-0650e21c5491

Same letter between Pascal and Christ. Huygens:
http://ckcc.huygens.knaw.nl/epistolarium/letter.html?id=huyg003/0562
https://gallica.bnf.fr/ark:/12148/bpt6k69975r/f284.image

These two go to the same transcription of a letter from Christ. Huygens to Dirck van Nierop
http://emlo.bodleian.ox.ac.uk/profile/work/e9be3850-23bc-45c6-9e99-fed34eaa640d
http://emlo.bodleian.ox.ac.uk/profile/work/1ef41629-117d-4dee-a2d3-2ad3e3207537

This one is the same part of a letter by Oldenburg quoted in a letter from Boyle:
http://emlo.bodleian.ox.ac.uk/profile/work/da9a9bd3-337e-4efe-acf5-de8d89acfe48
http://emlo.bodleian.ox.ac.uk/profile/work/d26367c2-b17f-4733-83d2-b4cbf31f763a

I have spotted one or two where they match because the date is non-specific but it has been filled in the 'standard gregorian date' field:
For example the below, first is marked as 'Early April' but '1659-04-30' in the standard date field and so it's a false duplicate.

http://emlo.bodleian.ox.ac.uk/profile/work/2735e4b4-a95a-48a2-b507-cc220fef02f2
http://emlo.bodleian.ox.ac.uk/profile/work/ba6474d3-a66b-459e-8736-29dc6c2475cb

Most of the duplicates are either 

Ussher printed edition - BCC
De Groot - Vossius catalogue
Vossius - BCC
Some Peiresc - Rubens
Some Huygens - Nierop

This may